The Success of College Basketball Teams can be predicted using several advanced team statistics

### 2022-04-24 Paper-On-NCAAB-Stats/outputs/paper/Paper-On-NCAAB-Stats.Rmd
prelim result section

Next, the slope coefficient for the true shooting percentage variable is 0.92, meaning that when all other predictor variables are held at a fixed value, if true shooting percentage increases by 1% then their simple rating system will increase by 0.92. Total rebound percentage has a slope coefficient even larger at 1.63. This coefficient value of 1.63 can be interpreted as how much a teams simple rating system increases by when their total rebound percentage goes up 1%. Both of these coefficients make sense as simple rating system will logically increase if a team shoots more efficiently and scores more points or if they grab more rebounds and get more attempts to score that their opposition, which was already determined by looking at the relation graphically earlier.

>>>>

WRITE MODEL HERE MAYBE AND TALK ABOUT HOW YOU ADD VALUES TO PREDICT SRS

Next, the slope coefficient for the true shooting percentage variable is 0.92, meaning that when all other predictor variables are held at a fixed value, if true shooting percentage increases by 1% then their simple rating system will increase by 0.92. Total rebound percentage has a slope coefficient even larger at 1.63. This coefficient value of 1.63 can be interpreted as how much a teams simple rating system increases by when their total rebound percentage goes up 1% and all other variables are fixed. Both of these coefficients make sense as simple rating system will logically increase if a team shoots more efficiently and scores more points or if they grab more rebounds and get more attempts to score that their opposition, which was already determined by looking at the relation graphically earlier. The estimated slope coefficient for turnover percentage is different from the other as it is negative, with a value of -2.04. This lines up with what was seen in the graphical analysis as simple rating system and turnover percentage have a negative relationship, since turning the ball over more will allow the other team to score more and lead to a worse SRS. This negative value tells us that when a teams turnover percentage increases by 1% and all other variables are held fixed, the teams simple rating system value will decrease by 2.04 units.

Table \@ref(tab:coefsum) also contains 95% confidence intervals. These intervals give us a range of plausible values for each estimate coefficient, and we are 95% certain that the true population parameter value is within this interval. For example, the true shooting percentage slope coefficient can reasonably be any value between 0.77 and 1.07, and our estimate coeffcient value of 0.92 for true shooting percentage falls right in the middle of this range. There is a chance this interval does not capture the true value but it is unlikely, as if we took 100 samples of college basketball data and created models, only 95% of the models and their confidence intervals for the estimated coefficients would capture the true population values. Fortunately, each of the estimated slope coefficients confidence intervals are quite narrow, as the lower and upper bounds only differ by 0.3, 0.31, and 0.45 respectively. The narrowness of the intervals is good as it means that our estimated coefficients are most likely quite accurate, and any coefficients and their confidence intervals that are estimated from other samples would give values very similar to the ones obtained from our sample that was used [@citeBassett]. The intercept coefficient also has a fairly narrow confidence interval as well, from -109.25 to -87.98, even if it may not seem like it relative to the other coefficients. This is because it is not dealing with percentage variables like the slope coefficient and instead has to do with simple rating system which has a wider range of values.

The final value in the summary table is the p-value of each estimated coefficient, which tell us how significant each estimated coefficient is. A low p-value, and one below 0.05 in particular, for a variables coefficient means that there is evidence against a null hypothesis stating the coefficient should be zero as the variable does not affect the response in the presence of the other variables in the model. Looking at the p-values for our coefficients, they are all extremely small and are very close to 0, meaning the null hypothesis is rejected and thus each of the coefficients are significant and belong in the model. However, this information must taken with a grain of salt, as p-values are difficult to work with since they assume all model assumptions are satisfied and the data was properly collected and cleaned [@citeRohan]. As a result of this, no decisions were made based on these values, but they do provide us with a piece of information that allow us to further see that the decision we did make are likely good ones due to their low values.

```{r}
library(plot3D)

scatter3D(ncaab_stats_train$ts_percent, ncaab_stats_train$trb_percent, ncaab_stats_train$srs, colvar = ncaab_stats_train$tov_percent, bty = 'b2',
          pch = 19, cex = 0.5, xlab = "TS%", ylab = "TRB%", zlab = "SRS", clab = "TOV%", ticktype = "detailed", )
```
